---
title: "CCProcessing Primer"
output: html_notebook
---

##1) Load library and set working directory.

```{r setup}
library(ccproc)

wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
knitr::opts_chunk$set(root.dir = dirname(rstudioapi::getActiveDocumentContext()$path))

```

##2) Set data directory and load file list.

```{r set_directory}
datadir <- "G:/Zeiss Confocal/Cellcounter Aggregation/cellcounter/New/"
filenames <- list.files(datadir)
files <- paste0(datadir,filenames)
```

##3) Load files into a new CellCounterDB object.

```{r load_files}
ccdb <- CellCounterDB$new(files)
```

##3A) Remove duplicate cell marks.

```{r remove_duplicates}
ccdb$remove_duplicates()
```


##4) Process raw data into features (crypts)

```{r feature_processing}
ccdb$processFeatures()
```

##5) Tag attributes based on filenames.

```{r tag_attributes}
ccdb$tag_attribute( Regex = "(TW[0-9]{2})", attribute = "Sample" )
```

##6) Verify feature detection with debug plots.

```{r debug_plots}
ccdb$plot_debug( names(ccdb$CCFiles), savedir = "G:/Zeiss Confocal/Cellcounter Aggregation/test/" )
```

##7) Save database object to file.

```{r save_db}
ccdb$save(file="ccdb")
```

##8) Call cells from specific rows, according to specific features.

```{r calling_data}
index <- ccdb$which_cells(list("Sample" = "TW28", "Position.Crypt" = 0:10, "Reg4-dsRed" = TRUE))
print(ccdb$cells[index,])
```


Adding functions to privately plot debugs amongst ones that need it. 
```{r more_debugging}
ccdb$metadata$run_debug <- TRUE
ccdb$metadata$debug_dir <- "G:/Zeiss Confocal/Cellcounter Aggregation/debug/"

to_debug <- c("IHC009 TW30-4R EphrinB1 005.lsm",
              "IHC009 TW30-6L Villin 005.lsm",
              "IHC009 TW30-7R ChgA 001.lsm",
              "TW21-29 IHC005 p-Histone3 5.czi")
ccdb$processFeatures(ccnames=to_debug)

ccdb$metadata$run_debug <- FALSE
```




```{r sandbox}

```

# New testline
