---
title: "CCProcessing Primer"
output: html_notebook
---

##1) Load library and set working directory.

```{r setup}
library(ccproc)

wd <- dirname(rstudioapi::getActiveDocumentContext()$path)
knitr::opts_chunk$set(root.dir = dirname(rstudioapi::getActiveDocumentContext()$path))

```

##2) Set data directory and load file list.

```{r set_directory}
datadir <- "G:/Zeiss Confocal/Cellcounter Aggregation/cellcounter/New/"
filenames <- list.files(datadir)
files <- paste0(datadir,filenames)
```

##3) Load files into a new CellCounterDB object.

```{r load_files}
ccdb <- CellCounterDB$new(files)
```

##3A) Remove duplicate cell marks.

```{r remove_duplicates}
ccdb$remove_duplicates()
```


##4) Process raw data into features (crypts)

```{r feature_processing}
ccdb$processFeatures()
```

##5) Tag attributes based on filenames.

```{r tag_attributes}
ccdb$tag_attribute( Regex = "(TW[0-9]{2})", attribute = "Sample" )
```

##6) Verify feature detection with debug plots.

```{r debug_plots}
ccdb$plot_debug( names(ccdb$CCFiles), savedir = "G:/Zeiss Confocal/Cellcounter Aggregation/test/" )
```

##7) Save database object to file.

```{r save_db}
ccdb$save(file="ccdb")
```

##8) Call cells from specific rows, according to specific features.

```{r calling_data}
index <- ccdb$which_cells(list("Sample" = "TW28", "Position.Crypt" = 0:10, "Reg4-dsRed" = TRUE))
print(ccdb$cells[index,])
```


Adding functions to privately plot debugs amongst ones that need it. 
```{r more_debugging}
ccdb$metadata$run_debug <- TRUE
ccdb$metadata$debug_dir <- "G:/Zeiss Confocal/Cellcounter Aggregation/debug/"

to_debug <- c("IHC009 TW30-4R EphrinB1 005.lsm",
              "IHC009 TW30-6L Villin 005.lsm",
              "IHC009 TW30-7R ChgA 001.lsm",
              "TW21-29 IHC005 p-Histone3 5.czi")
ccdb$processFeatures(ccnames=to_debug)

ccdb$metadata$run_debug <- FALSE
```




```{r sandbox}
# This file is the only one currently with unassigned cells, so using as a test case. 
img = "IHC009 TW30-3R Reg4 001.lsm"
cc <- ccdb$CCFiles[[img]]$cells
tri <- ccdb$CCFiles[[img]]$metadata$triangulation
crypt.ind <- unique(ccdb$cells[which(ccdb$cells$Image==img),"Crypt"])
crypt.ind <- crypt.ind[crypt.ind>0]
crypts <- list()
for(i in 1:length(crypt.ind)){
  crypts[[i]] <- ccdb$crypts[[crypt.ind[i]]]$cells
}
unassigned_sets <- list(c(137,136,135,134,133,132))

# Assign unassigned sets by relinking with separated crypts.
          # TODO
          # '
          # ' Basic workflow to construct:
          # '   - Loop through unassigned sets
          # '   - Look for connections between endpoints in established crypts and any in unassigned set.
          # '   - Determine optimal connection points based on angular and distance strain.
          # '   - Merge vectors in order based on above.
          # '   - Re-cut into separate crypts.
          
          if(length(unassigned_sets)>0){
            while(!all(unlist(lapply(unassigned_sets,function(x){is.null(x)})))){
              
              # First, pull all the endpoints from established crypts.
              endpoints <- c()
              for(i in crypts){
                endpoints <- c(endpoints,i[1],i[length(i)])
              }
              
              # Grab set. Looping by nullifying as going through. 
              to_grab <- which(!unlist(sapply(test,function(x){is.null(x)})))[1]
              set <- unassigned_sets[[to_grab]]
              unassigned_sets[[to_grab]] <- NULL
              # Should extract candidate vertices from set
              testedges <- matrix(c(rep(set,each=length(endpoints)),rep(endpoints,times=length(set))),ncol=2)
              edges <- private$areEdges(testedges,tri$E)
              edges <- edges[edges>0]
              # Picks a start edge based on minimum distance * theta
              start.edge <- tri$E[edges[order(tri$E.beta[edges] * tri$E.dist[edges])[1]],]
              # Pull index from unassigned for start edge
              set.start.index <- which(set %in% start.edge[start.edge %in% set])
              # End point should be adjacent in ordered vector, with looping assumed.
              set.end.candidates <- set[c((length(set) + set.start.index + 1) %% length(set),(length(set) + set.start.index - 1) %% length(set))]
              # From candidates, determine which edge is the most likely fit.
              edge.candidates <- tri$E[edges,][private$which_vert(set.end.candidates,tri$E[edges,]),]
              edge.candidate.index <- private$areEdges(edge.candidates,tri$E)
              end.edge <- tri$E[edge.candidate.index[order(tri$E.beta[edge.candidate.index] * tri$E.dist[edge.candidate.index])[1]],]
              set.end.index <- which(set %in% end.edge[end.edge %in% set])
              # Cycle and orient vector to merge with others.
              set.start <- set[set.start.index]
              set.end <- set[set.end.index]
              set <- private$cycle_vector(set,set.start)
              if(set.end != set[length(set)]){
                set <- private$cycle_vector(set[length(set):1],set.start)
              }
              
              # Figure out which crypt sets to pull.
              crypt.start <- ceiling((1:length(endpoints))/2)[which(endpoints %in% start.edge[start.edge %in% endpoints])]
              crypt.end <- ceiling((1:length(endpoints))/2)[which(endpoints %in% end.edge[end.edge %in% endpoints])]
              
              if(crypt.start == crypt.end){
                cryptset <- crypts[[crypt.start]]
                # Reorient cryptset vector 
                if(which(cryptset %in% start.edge) != length(cryptset)){
                  cryptset <- cryptset[length(cryptset):1]
                }
                crypts[[crypt.start]] <- private$cut_open_crypt(c(cryptset,set),cc,dist.mean,dist.sd,tri$E)
              }else{
                # Process as per prior splitting method. Expecting two crypts so fixed output.
                crypt1 <- crypts[[crypt.start]]
                crypt2 <- crypts[[crypt.end]]
                # Reorient crypt vectors
                if(which(crypt1 %in% start.edge) != length(crypt1)){
                  crypt1 <- crypt1[length(crypt1):1]
                }
                if(which(crypt2 %in% end.edge) != 1){
                  crypt2 <- crypt2[length(crypt2):1]
                }
                set <- c(crypt1,set,crypt2,crypt1[1])
                
                # Copy paste from previous cleaving algorithm. TODO: Try to get into a separate function to modularize. 
                origins <- cc$metadata$OriginCells[cc$metadata$OriginCells %in% set]
                set <- private$cycle_vector(set,origins[1])
                cleavepoints <- c()
                ind_or <- sort(which(set %in% origins))
                # Looks for cleave points between origins.
                for(j in 1:(length(ind_or)-1)){
                  subset <- set[ind_or[j]:ind_or[j+1]]
                  cut_point <- private$find_cut_point(subset,cc,dist.mean,dist.sd,tri$E)
                  cleavepoints <- c(cleavepoints,
                                    which(set==subset[cut_point])[1],
                                    which(set==subset[cut_point])[1]+1)
                }
                # Break loop around first cleavepoint and adjust set vector
                set <- set[-length(set)]
                set <- private$cycle_vector(set,set[cleavepoints[2]])
                cleavepoints <- cleavepoints[-(1:2)]-cleavepoints[1]
                # Set up paired indices of start and endpoints for each set in a 2-column matrix
                cleavepoints <- matrix(c(1,cleavepoints,length(set)),ncol=2,byrow=TRUE)
                set[cleavepoints[j,1]:cleavepoints[j,2]]
                crypts[[crypt.start]] <- private$list_append(crypts,set[cleavepoints[1,1]:cleavepoints[1,2]])
                crypts[[crypt.end]] <- private$list_append(crypts,set[cleavepoints[2,1]:cleavepoints[2,2]])
              }
            }
          }
        


which_vert = function(i,x){
      # Returns which vertices in set x contain indices i. Assumes vertices are rows.
      return(which(rowSums(matrix(x %in% i,ncol=ncol(x)))>0))
}

isEdge = function(vector,edgeset){
  # Returns index of edge formed by vector components in edgeset, or 0 if not in edgeset.
  tryCatch(
    {
      index = (base::rowSums((edgeset==vector[1])+(edgeset==vector[2]))==2)
      if(any(index)){
        return(which(index))
      }
      else{
        return(0)
      }
    },
    error = function(e){message("Error in isEdge: vector must be length 2.")},
    warning = function(w){}
  )
}

areEdges = function(m,edgeset){
  # Returns index of edge formed by vector components in each row of matrix m in edgeset, or 0 if not in edgeset.
  # m is a matrix with 2 columns.
  # A mapply wrapper for isEdge.
  tryCatch(
    {
      return(mapply(function(v1,v2){isEdge(c(v1,v2),edgeset)},
                    v1=m[,1],
                    v2=m[,2]))
    },
    error = function(e){message("Error in areEdges: Matrix not compatible.")},
    warning = function(w){}
  )
}


cycle_vector = function(v,i){
  # Cycles vector so that value i is at position 1 (and pos(last) if looped)
  if(v[1]==i){
    return(v)
  }else if(v[1]==v[length(v)]){
    return(c(v[which(v==i):length(v)],v[2:(which(v==i)-1)],i))
  }else{
    return(c(v[which(v==i):length(v)],v[1:(which(v==i)-1)]))
  }
}

find_cut_point = function(v,cc,dist.mean,dist.sd,edges){
      # Returns the optimal cut point in an ordered vector
      # Inputs:
      # v = ordered vector describing points.
      # cc = cellcounter object
      # edges = edges E from a triangulation object
      # dist.mean = mean distance between points
      # dist.sd = sd of distance between points
      testfwd <- log(1:length(v))
      testrev <- log(length(v):1)
      angular_strain <- pi - private$rolling_angle(v,cc)
      dist_strain <- exp((private$rolling_dist(v,cc)-dist.mean)/dist.sd)
      # Checks that edges are present in Delaunay triangulation, applies strong penalty if not.
      edgecheck <- (c(private$areEdges(private$vector_to_edges(v),edges),1)==0)*100000
      test_stat <- testfwd*testrev*angular_strain*angular_strain*dist_strain + edgecheck
      return(order(test_stat,decreasing=TRUE)[1])
    }

    cut_open_crypt = function(v,cc,dist.mean,dist.sd,edges){
      i0 <- cc$metadata$OriginCells[cc$metadata$OriginCells %in% v]
      # Cycle vector to origin and make loop.
      v <- private$cycle_vector(v,i0)
      if(v[1]!=v[length(v)]){
        v <- c(v,v[1])
      }
      # Test to verify optimal opening point for crypt.
      cut_point <- find_cut_point(v,cc,dist.mean,dist.sd,edges)
      v <- c(v[(cut_point+1):(length(v)-1)],v[1:cut_point])
      return[v]
    }

```

# New testline
